Earth at night*\\ {\footnotesize \textsuperscript{*}The visualisation of average radiance in specific area}

### 2021-09-17 paper/main.tex
fix

\subsection{Overview of World Bank Light Every Night}
World Bank Light Every Night \cite{WorldBan13:online} is a comprehensive data repository of light satellite images collected at night by 
two sensors for the past 30 years: National Defense Meteorological Satellite Program (DMSP) Line of Business Scanning 
System (OLS), data from 1992 to 2017.Visible infrared imaging radiometer suite (VIIRS) day and night band (DNB) data are 2012-2020.

Both DMSP-OLS and VIIRS-DNB sensors capture various low-light emission sources from the earth as optical data. These light source 
data mainly include brightness data generated by various human activities, such as city lights, gas flares, fishing boats, and 
agricultural fires, and also capture other natural light phenomena at night, such as aurora. The data repository is released and 
can be used for analysis. The data repository was established by the World Bank in cooperation with the National Oceanic and Atmospheric 
Administration (NOAA) and the University of Michigan. Most of the basic data come from the NOAA National Environmental Information 
Center (NCEI) file.

After continuous exploration, development, updates, and upgrades, the University of Michigan’s additional processing supports access 
in cloud-optimized GeoTIFF format (COG) and searches using Spatio-temporal Asset Catalog (STAC) standards. The ever-improving standards 
facilitate the analysis and become part of the ready data ecosystem, which is improving access to geospatial data sets, which makes it 
more widely accepted by the public and can be easily discovered, processed, and analyzed Geospatial data. Our project data will also use 
cloud-optimized GeoTIFF format (COG) and STAC standards to implement network-level applications.

\subsection{Remote sensing}
Research by NASA shows that modern remote sensing technology began with the invention of the camera more than 150 years ago. The 
first original photo appeared as a "still image", but it inspired people's ideas and practices for shooting and looking down on 
the surface of the earth. This idea appeared in the 1840s. The first photos were used for topographic mapping. Later in the First 
World War, the cameras mounted on the aircraft provided a bird's-eye view of a considerable surface area and provided a large amount 
of terrain data for military activities. After continuous research and development, the current remote sensing technology has reached 
a qualitative leap. It is now commonly used to describe the science and art of identifying, observing, and measuring objects without 
directly touching them. The process involves detecting and measuring radiation of different wavelengths reflected or emitted from distant 
objects or materials, through which they can be identified and classified by category/type, substance, and spatial distribution \cite{earthdata28:online}.

\subsubsection{Orbits}

@@

Polar-orbiting satellites (Fig.~\ref{satellites}) are located in an orbital plane that is nearly 90 degrees inclined to the equatorial 
plane. This tilt allows the satellite to perceive the entire earth, including polar regions, to observe locations that are difficult 
to reach from the ground. Many polar-orbiting satellites are considered sun-synchronous, which means that the satellite passes through 
the same position at the same solar time in each cycle. The polar orbit can be ascending or descending. In an ascending orbit, the satellite 
moves from south to north as it passes the equator. In descending orbit, the satellite moves from north to south.

@@

Low Earth Orbit (LEO) (Fig.~\ref{LEO})is an orbit relatively close to the surface of the earth. It is usually located at an altitude of fewer than 
2000 kilometers, but it may be as low as 400 kilometers above the earth. Compared to other orbits, it is low, but still far from the 
surface of the earth \cite{earthdata28:online}.It is the most commonly used orbit for satellite imaging because it is possible to take 
higher resolution images close to the surface. It is also the orbit used by the International Space Station (ISS) because it is easier 
for astronauts to travel to and from it at shorter distances. The satellite in this orbit travels at a speed of about 7.8 kilometers per 
second; at this speed, it takes about 90 minutes for the satellite to orbit the earth, which means that the International Space Station 
orbits the earth about 16 times a day \cite{ESAkerne12:online}.

@@

\paragraph{Geostationary}

The orbit of a geostationary satellite (Fig.~\ref{Geostationary}) can only be achieved at an altitude very close to 35,786 kilometers, and the satellite can 
be fixed at one longitude of the equator. There are hundreds of communication satellites and several weather satellites in such orbits.

@@

\paragraph{Electromagnetic Spectrum} 
The electromagnetic spectrum (Fig.~\ref{Spectrum})is a graph of electronic signals distributed according to frequency or wavelength \cite{electrom75:online}. Although all electromagnetic waves travel at the speed of light in vacuum, they have a wide range of frequencies, wavelengths, and photon energies. The entire electromagnetic spectrum is divided into radio waves, infrared radiation, visible light, ultraviolet radiation, X-rays, and gamma rays, but people are far away in gamma rays, so we will not discuss them. Due to the different emission, transmission and absorption of different waves, they have different practicability and practical range.

@@

Low Frequency (LF): Low frequency refers to the radio frequency (RF) in the range of 30 kHz–300 kHz. Low\-frequency AM 
broadcasting services are widely used in Northern Europe, North Africa, and Asia. In the current era, its main uses are 
aircraft beacons, navigation (LORAN), information, and weather systems. Numerous time signal stations such as MSF, DCF77, 
JJY, and WWVB are located in this frequency band, which is also called the kilometer band or kilometer wave \cite{httpswww63:online}.

Medium Frequency (MF): Medium Frequency means radio frequency (RF) in the range of 300 kHz to 3000 kHz. For example, 
the AM broadcast band is a medium wave (MW), and the MF band is also called the 100-meter band, which ranges from 100 
to 1000 hundred meters \cite{httpswww49:online}.

High Frequency (HF): The wave frequency of the high-frequency electromagnetic field is between 300 MHz and 3 GHz, and the 
wavelength is from 1 m to 10 cm. It is mainly human-generated non-ionizing electromagnetic radiation, which does not occur 
naturally in the environment, excluding low-amplitude VHF (Very high frequency) cosmic radiation. With the rapid development 
of wireless technology, HF is increasingly appearing in the environment.

@@

Very high frequency (VHF) is ITU's electromagnetic wave in the range of 30 to 300 megahertz (MHz), and the corresponding 
wavelength is ten meters to one meter (Wikimedia Foundation \cite{Veryhigh48:online}.

Ultra-high frequency (UHF) is the ITU's 300 megahertz (MHz) and 3 gigahertz (GHz), also known as the decimeter band because 
the wavelength ranges from one meter to one-tenth of a meter. UHF radio waves propagate mainly through the line of sight; 
they can be blocked by various objects, and their transmission capacity will be limited by the blocking of objects. For example, 
TV broadcasting, mobile phones, GPS, WIFI, and walkie-talkies all use UHF to realize the dissemination and communication of data 
information \cite{Ultrahig37:online}.

Super High Frequency (SHF): The Super High Frequency (SHF) range is ITU to 3 to 30 gigahertz (GHz). This frequency belongs to 
the microwave band, so radio waves with these frequencies are called microwaves. There are many devices in this frequency range, 
such as radar transmitters, wireless local area networks, satellite communications, and it is also used in industrial microwave 
heating, medical diathermy, and microwave hyperthermia to treat cancer \cite{Superhig8:online}.

Extremely high frequency (EHF) is a radio frequency in the electromagnetic spectrum from 30 to 300 gigahertz (GHz). Its frequency 
is between the ultra-high frequency band and the far-infrared frequency band, and below it is the terahertz frequency band. The 
wavelength of radio waves in this band varies from ten to one millimeter, so it is also called the millimeter-wave band and the 
radiation in its waveband is called millimeter waves \cite{Extremel31:online}.

@@

The visible light spectrum is the segment of the electromagnetic spectrum that the human eye can view. Its wavelengths are 
380 to 700 nanometers.The full spectrum of visible light can be divided into rainbow colors because each color has a different 
wavelength. Violet has the shortest wavelength, about 380 nanometers, and red has the longest wavelength, about 700 nanometers \cite{Vis73:online}.

@@

UV (ultraviolet) light refers to the region of the electromagnetic spectrum between visible light and X\-rays, with a wavelength 
between 400 and 10 nanometers. Among ultraviolet rays, red is the light with the longest wavelength, and violet is the light 
with the shortest wavelength. Therefore, the light with the longest wavelength is called infrared light, and the light with the 
shortest wavelength is called ultraviolet light \cite{uvlight14:online}.

@@

X\-rays are a penetrating form of high-energy electromagnetic radiation. The wavelength range of most X\-rays is 10 picometers 
to 10 nanometers, the corresponding frequency range is 30 terahertz to 30 hertz (30×1015 Hz to 30×1018 Hz), and the energy range 
is 124 eV to 124 keV (Wikimedia Foundation \cite{XrayWiki61:online}.

@@

    \begin{itemize}
        \item Low resolution: more than 60m/pixel 
        \item Medium resolution: 10 ‒ 30m/pixel 
        \item High resolution to ultra-high resolution: 30cm ‒ 5m/pixel
    \end{itemize}

@@

Running "make deploy" in the directory show as Fig.~\ref{cf2}, which is "A2/deploy/roles/mysql/templates", can create a slave RDS MySQL instance. Because 
a cross-region database replica is needed in this demo, running "make master" can build another master RDS MySQL after changing the aws-cli region. And the 
slave instance is replicated instantly from the master instance. Both of the commands for MySQL are using CloudFormation. The first one is just a very 
simple process, but the second one is also generating a Lambda function to rotate the MySQL password in the master database, and store it in Secrets Manager service.

@@

\subsection{Imagery Overview}
The Resources on AWS is Light Every Night dataset of all VIIRS DNB and DMSP-OLS nighttime satellite data. Resource type is S3 Bucket. 
Amazon Resource Name (ARN) is arn:aws:s3:::globalnightlight. AWS Region is us-east-1. AWS CLI Access is no AWS account required, and 
command is "aws s3 ls s3://globalnightlight/ --no-sign-request" \cite{WorldBan13:online}.

@@

For example: F12199501010014.night.OIS

@@

For example: SVDNB\_npp\_d20150504\_t1335358\_e13411
62\_b18219\_c20150504194116381040\_noaa
\_ops.rade9.co.tif. The file structure is:

\begin{itemize}
    \item npp\_d20150504\_t1335358\_e1341162\_b18219
    \item npp = satellite ID
    \item d20150504 = start date of first scan in aggregate \\
    (2015/05/04)
    \item t1335358 = time of first scan (13:35:35.8)
    \item e1341162 = time of last scan (13:41:16.2)
    \item b18219 = orbit number of first scan
\end{itemize}

@@

The SpatioTemporal Asset Catalog (STAC) specification provides a common language to describe a series of geospatial 
information in order to provide easier indexing and searching. A "space\-time asset" is any file that represents information 
about the Earth captured in a specific space and time. The STAC specification is to allow all providers to publish new data 
sets or APIs without writing new code when they are published as a spatiotemporal asset catalog \cite{SpatioTe21:online}. 
First of all, for providers, STAC is a standardized method for exposing Spatio\-temporal data collections while cataloging 
assets and STAC is also a unified asset indexing method. Second, developers can build infrastructure to host, ingest, or 
manage spatial data collections, and can be extended to customize domains. Finally, data consumers often have to build a 
unique pipeline for each different data set they use.

>>>>

\subsection{Overview of World Bank Light Every Night}
World Bank Light Every Night \cite{WorldBan13:online} is a comprehensive data repository established by the World Bank in collaboration with the National Oceanic and Atmospheric Administration (NOAA) and the University of Michigan, which contains light satellite images collected at night over the past 30 years. Two sensors have been in continuous use until now: the first is the Defense Meteorological Satellite Program (DMSP) line of business scan
System (OLS), its data collection is from 1992-2017 data. The other is the Visible Infrared Imaging Radiometer Suite (VIIRS) Day and Night Band (DNB). Its main data collection is from 2012-2020.

Both DMSP-OLS and VIIRS-DNB sensors use different wavelengths on the satellite to collect various light sources on the earth as optical data. These light source data mainly include brightness data generated by various human activities. Most of the light comes from cities, fishing boats, fires, or other natural light. It is a long process for the continuous light source data to be collected and stored. However, most of the basic data comes from the NOAA National Environmental Information Center (NCEI). Finally, all the data will be provided to the public as a shared database for analysis and use.

After continuous exploration, development, updates and upgrades, the University of Michigan supports access to Cloud-optimized access to GeoTIFF format (COG) files through additional processing, and also uses the Spatio-temporal Asset Catalog (STAC) standard to edit data for sharing File, and data sharing is ready. The ever-improving standards promote the integration of data to the integrity of the shared ecosystem, which is improving access to geospatial data sets, which makes it more widely accepted by the public and can easily discover, process, and analyze geospatial data. Our project data will also use cloud-optimized GeoTIFF format (COG) and STAC standards to implement network-level applications.

\subsection{Remote sensing}
NASA's research shows that modern remote sensing technology began with the invention of the camera more than 150 years ago \cite{earthdata28 :online}. The first original photo appeared in the form of a "still image", but it inspired the idea and practice of people taking pictures and looking down on the surface of the earth. This idea appeared in the 1840s. The first photo was used for topographic mapping. At the end of the First World War, the cameras installed on the aircraft provided a bird's-eye view of a considerable area and provided a large amount of terrain data for military activities. After continuous research and development, the current remote sensing technology has reached a qualitative leap.

Remote sensing technology is usually used to describe objects, without direct contact, only to identify, observe and measure. Most of the data in this project comes from the detection and measurement of radiation of different wavelengths reflected or emitted from distant objects or materials. Through these radiations, they can be identified and classified by category, substance and spatial distribution\cite{earthdata28 :online}Finally determine the wavelength of the light to image.

\subsubsection{Orbits} 
Here are the 3 most commonly used orbits used to observe the changes of the earth and data collection, polar orbiting satellites, low-Earth orbit, and geostationary. More explanations and details will be elaborated below:

@@

Polar orbiting satellites (picture ~\ref{satellites}) have an orbit close to 90 degrees to the equator. This angle allows the satellite to better perceive and observe the earth, so that more data can be collected more simply and in detail. Including polar regions and some areas where it is difficult to collect data\WhatisRe36:online}. Most of the NOAA polar satellites mentioned in the project provide infrared and visible light earth image data. Sometimes they also collect some data on the atmosphere\cite{side357:online}. Most polar-orbiting satellites are sun-synchronous. This is to allow the satellites to pass the same position at the same solar time in each cycle. Such satellites will also reach the Antarctic and North Pole in different orbits to collect meteorological, ocean, land, climate and other professional data.

@@

Low Earth Orbit (LEO) (picture ~\ref{LEO}) is the closest orbit to the earth for a satellite. It is only less than 400 kilometers above the surface of the earth, but it may be even higher than 2000 kilometers. Range \cite{WhatisRe36:online}. Such low-orbit operation has inherent advantages for satellites in shooting satellite maps and navigation, etc. \cite{earthdata28:online}. The current high-resolution images are basically taken by it, and such an orbit is also the orbit used by the International Space Station (ISS). This design makes it easier for astronauts to travel to and from it. The satellite in this orbit moves at a speed of about 7.8 kilometers per second; it only takes 90 minutes for a satellite to orbit the earth at this speed, which means that the International Space Station orbits the earth approximately 16 times a day, which is also useful for satellite maps and satellite positioning. Provides a better experience\cite{ESAkerne12:online}.

@@

\paragraph{Geostationary}
The orbit of a geostationary satellite (picture ~\ref{Geostationary}) can only be achieved at an altitude very close to 35,786 kilometers, and the satellite can be fixed at one longitude of the equator \cite{Synchron89:online}. Such a satellite will be a place far away from the earth to observe and collect data. At the same time, it will be able to cover an area on the earth for a long time and continuously because of its location. For example, a weather satellite will operate in such an orbit. \Cite{WhatisRe36:online}. As far as the earth is concerned, the satellite operating in this way is stationary, its trajectory is synchronized with the earth, and its rotation period is also synchronized with the earth\cite{CelesTra70:online}.

@@

\paragraph{Electromagnetic Spectrum} 
The electromagnetic spectrum (picture ~\ref{Spectrum}) is a picture \cite{electrom75:online}. According to the frequency or wavelength distribution of electronic signals. These electronic frequencies or waves all travel at the speed of light in vacuum, but their frequencies, wavelengths, and photon energies are all different and have a wide range. The entire electromagnetic spectrum is divided into 7 types, radio waves, infrared radiation, visible light, ultraviolet radiation, X-rays and gamma rays. For gamma rays, it is still relatively far away from people in reality, so we will not discuss them. Therefore, the following part will give an introduction to the different emission, transmission and absorption of different waves, as well as their different practicability and scope of application, so as to have a better understanding of our project.

@@

Low Frequency (LF): Low frequency refers to the radio frequency in the range of 30 kHz–300 kHz \cite{httpswww63:online}. Low\-frequency AM broadcasting services are widely used in Northern Europe, North Africa, and Asia. In the current era, its main uses are aircraft beacons, navigation, information, and weather systems.

Medium Frequency (MF): Medium Frequency means radio frequency (RF) in the range of 300 kHz to 3000 kHz \cite{httpswww49:online}. For example, 
the AM broadcast band is a medium wave (MW), and the MF band is also called the 100-meter band, which ranges from 100 
to 1000 hundred meters.

High frequency (HF): The wave frequency of the high frequency electromagnetic field is between 300 MHz and 3 GHz, and the wavelength is 1 m to 10 cm \cite{Highfreq56:online}. High-frequency electromagnetic fields do not occur in nature, so these electromagnetic fields are mainly man-made. With the rapid development of technology, among wireless technologies, high-frequency waves are more widely used, such as high-frequency communication. Such technologies can achieve the same call effect as satellites or telephones\cite{WhatisHi8:online}.

@@

Very high frequency (VHF) is ITU's electromagnetic wave in the range of 30 to 300 megahertz (MHz), and the corresponding 
wavelength is ten meters to one meter \cite{Veryhigh48:online}.

Ultra high frequency (UHF) has a wave frequency between 300 MHz and 3 GHz because the wavelength ranges from one meter to one tenth of a meter\cite{Ultrahig37:online}. Such UHF radio waves mainly propagate through the line of sight; however, they can be blocked by objects resulting in limited transmission capacity, so they are usually used for air traffic control air-to-ground voice communication or other transmissions such as TV broadcasts, WIFI, and walkie-talkies. Data dissemination and information communication\cite{UltraHig10:online}.

The wave frequency range of super high frequency (SHF) is 3 to 30 GHz \cite{Superhig8:online}. This frequency is also called the microwave frequency band. In this frequency range, many technologies have been invented, such as microwave oven technology, radar technology, wireless network technology, satellite communication technology, etc. Their realization and development are all related to wave frequency research. relation. These studies also provide people with great convenience and efficient quality of life.

Extremely high frequency (EHF) is a radio frequency in the electromagnetic spectrum from 30 to 300 GHz. It is a frequency between the ultra-high frequency band and the far-infrared frequency band. The wavelength of this radio wave band ranges from ten millimeters to one millimeter, so it is also called the millimeter wave band\cite{Extremel31:online}. Its transmission will be hindered by the atmosphere, so its transmission and rebroadcasting distance is very short, which also reduces its usability. This has also become the main obstacle to its development and use.

@@

The visible spectrum is the part of the electromagnetic spectrum that the human eye can see, so it is also called the visible wave. For such a wave, its wavelength is usually between 380 and 700 nanometers. The rainbow is a kind of light wave in space. There are seven colors. Because each color is different, their wavelengths are also different. The purple wavelength is the shortest. About 380 nanometers, the red wavelength is the longest, about 700 nanometers\cite{Vis73:online}.

@@

UV (ultraviolet) light refers to the region of the electromagnetic spectrum between visible light and X\ rays, with a wavelength between 400 and 10 nanometers \cite{uvlight14:online}. Among ultraviolet rays, red light has the longest wavelength, while violet light has the shortest wavelength. Therefore, the longer wavelength is called ultraviolet light, and the shorter wavelength is called ultraviolet light. Nowadays, the use of ultraviolet light can be seen everywhere, such as the invention of the currency detector, and the medical application of ultraviolet light shows its value.

@@

X\ ray is a penetrating form of high-energy electromagnetic radiation. The wavelength range of most X\ rays is 10 picometers to 10 nanometers, the corresponding frequency range is 30 THz to 30 Hz, and the energy range is 124 eV to 124 keV \cite{XrayWiki61:online}. X-rays are also used for physical examination and diagnosis in modern medicine because of X-ray imaging technology. When the light beam passes through the body, different shades of bone, metal, or other materials will be formed due to the different density of the material, thus forming an image \cite{XrayImag8:online}.

@@

    \begin{itemize}
        \item Low resolution: over 60m/pixel 
        \item Medium resolution: 10 ‒ 30m/pixel 
        \item High resolution ‒ ultra-high resolution: 30cm ‒ 5m/pixel
    \end{itemize}

@@

Running "make deploy" in the directory shown as Fig.~\ref{cf2}, which is "A2/deploy/roles/mysql/templates", can create a slave RDS MySQL instance. Because 
a cross-region database replica is needed in this demo, running "make master" can build another master RDS MySQL after changing the aws-cli region. And the 
slave instance is replicated instantly from the master instance. Both of the commands for MySQL are using CloudFormation. The first one is just a very 
simple process, but the second one is also generating a Lambda function to rotate the MySQL password in the master database, and store it in Secrets Manager service.

@@

\subsection{Imagery Overview}
The resource on AWS is the Light Every Night dataset of all VIIRS DNB and DMSP-OLS night satellite data. Its resource type is S3 Bucket on AWS cloud server. People can directly access files on Amazon cloud service through arn:aws:s3::globalnightlight, and its region is us-east-1\cite{WorldBan13:online}.

@@

For example: this is a file from database called F12199501010014.night.OIS， and lots of information will be given to this file.

@@

The file example of data is called: 
SVDNB\_npp\_d20150504\_t1335358\_e13411
62\_b18219\_c20150504194116381040\_noaa
\_ops.rade9.co.tif. The file structure is:
Then there are lots details about what them are.
\begin{itemize}
    \item npp\_d20150504\_t1335358\_e1341162\_b18219
    \item npp = satellite ID
    \item d20150504 = start date of first scan in aggregate \\
    (2015/05/04)
    \item t1335358 = time of first scan (13:35:35.8)
    \item e1341162 = time of last scan (13:41:16.2)
    \item b18219 = orbit number of first scan
\end{itemize}

@@

The SpatioTemporal Asset Catalog (STAC) specification uses a common language to describe geospatial information to provide easier indexing and searching\cite{SpatioTe21:online}. "Space-time assets" is a kind of specific information to mark the file with the earth information data captured in different specific spaces and times. These data marked by the STAC specification will be published by the provider as a spatiotemporal asset catalog without the need to write new code collections or APIs. First of all, for providers, STAC is a standardized method, used to disclose spatiotemporal data collection assets when cataloging, and STAC is also a unified asset index method. Second, developers can build infrastructure to host, ingest, or manage spatial data collections, and can extend to custom domains. Finally, data consumers often have to build a unique pipeline for each different data set they use.
